Instructions for developing new pages for the MarineOmics webpage

### 2023-12-15 DRAFT_lncRNA.Rmd
lncRNA download

## Notes on running code. This workflow is written such that a user an fully reproduce the code. Th

>>>>

## Notes on running code. This workflow is written such that a user an fully reproduce the code.

# Downloading data

The data used for this workflow is from Acropora pulcra, and part of the E5 (https://e5coral.org) project. see https://github.com/urol-e5/deep-dive for more details.

```{r, engine='bash'}
mkdir ../data/lncRNA

wget -r \
--no-directories --no-parent \
-P ../data/lncRNA \
-A "*fastq.gz" https://gannet.fish.washington.edu/Atumefaciens/20230519-E5_coral-fastqc-fastp-multiqc-RNAseq/A_pulchra/trimmed/

```
